Model Checking Differentially Private Properties

### 2018-06-06 semantics-mdp.tex
Write something on experiments

\todo{explain experiments}

>>>>

We model Algorithm~\ref{algorithm:online-model} as in Section~\ref{subsec:threshold} 
and apply implementation on model checking to check whether the
mechanism is differentially private. An advantage of model checking is that we
can check property of any exact value of parameters $\epsilon$ and $\delta$.
On the one hand,
smaller values for particular neighborhood database could be obtained.
For instance, for the state $t_3r_5$ and its neighborhood state $\underline{t}_3\underline{r}_4$, we verify the state
satisfies the property $\bigwedge_{k \in \bbfZ^{\geq 0}} \dpriv{0}{0.17} ((\X^k\bot) \top)$(Note that with k rising, the reachability probability decreases to approximately 0).
On the other hand, we could verify that for all the neighborhood database, i.e, the neighborhood states, the property $\bigwedge_{k \in \bbfZ^{\geq 0}} \dpriv{1}{0.74} ((\X^k\bot) \top)$ is satisfied. This indicates that the mechanism in Algorithm~\ref{algorithm:online-model} is differential private with $\epsilon = 1$ and $\delta = 0.74$. The parameter $\delta$ here seems large, due to the fact that 
Propsition~\ref{proposition:sufficient-condition-mdp-model-checking} is a sufficient 
condition.
